### 2020-01-11 paper/paper.tex
notes to self

The method we propose here---\name---embodies these ideas.
It is a non-parametric, hierarchical, data-driven model for the
wavelength solution.
By being non-parametric, it delivers enormous freedom to the
wavelength solution to match or adapt to any instrument or detector
oddities.
By being hierarchical, it restricts that freedom tremendously, but it
does so appropriately for the observed variations in the
spectrography.
\name\ is designed for temperature-controlled, bench-mounted, fiber-fed
spectrographs with good calibration sources, such as laser-frequency
combs, etalons, or good arc lamps.
We have in mind the \eprv\ instruments and \eprv\ science cases.
But we expect \name\ to have applications for other kinds of
spectrographs in other contexts.

\section{Method} \label{sec:method}
We operate on the core idea that the wavelength solution is living in a low-dimensional space, where the degrees of freedom are set by the limited degrees of freedom of the spectrograph hardware.

We will pose the problem in the following way.  Given an exposure $n$, and order $m$, there is a relationship between
the two-dimensional $(x,y)$-position on the detector and the
wavelength $\lambda$
\begin{equation}
\lambda(x,y,m,n) = f(x,y,m;\theta_{n})
\quad ,
\end{equation}
where $\theta_{n}$ is a big blob of parameters for this exposure.

>>>>

The method we propose here---\name---embodies these ideas.
It is a non-parametric, hierarchical, data-driven model for the
wavelength solution.
By being non-parametric, it delivers enormous freedom to the
wavelength solution to match or adapt to any instrument or detector
oddities.
By being hierarchical, it restricts that freedom tremendously, but it
does so appropriately for the observed variations in the
spectrograph.
\name\ is designed for temperature-controlled, bench-mounted, fiber-fed
spectrographs with good calibration sources, such as laser-frequency
combs, etalons, or good arc lamps.
We have in mind the \eprv\ instruments and \eprv\ science cases.
But we expect \name\ to have applications for other kinds of
spectrographs in other contexts; the motivating ideas behind this
project are true for almost every astronomical spectrograph.

\section{Method} \label{sec:method}
We operate on the two core ideas that the wavelength solution should be given enormous flexibility, but that in fact it will be living in a very low-dimensional space, where the degrees of freedom are set by the limited kinematics of the spectrograph hardware.

HOGG: THIS IS NOW ALL WRONG... We will pose the problem in the following way.  Given an exposure $n$, and order $m$, there is a relationship between
the two-dimensional $(x,y)$-position on the detector and the
wavelength $\lambda$
\begin{equation}
\lambda(x,y,m,n) = f(x,y,m;\theta_{n})
\quad ,
\end{equation}
where $\theta_{n}$ is a big blob of parameters for this exposure.
